```{r echo = FALSE}
# knitr::opts_chunk$set(comment=NA, cache=FALSE, message=FALSE, warning=FALSE)
# suppressMessages(library(radiant))
# uncomment the lines above to 'knit' the Rmd file in Rstudio
# you will also need to load the data using load()
```

## Sample report

This is an example of the type of report you can write in Radiant.

* You can create
* bullet lists

1. And numbered
2. lists

### Math

You can even include math if you want: $f(alpha, eta) propto x^{alpha-1}(1-x)^{eta-1}$.

To show the output press the `Update` button.

### Documenting analysis results in Radiant

When you click the book icon on a page the browser will bring you
to this report page. By default Radiant will paste the code generated
for the analysis you just completed at the bottom of the report.
However, you can turn off that feature by clicking the `Manual paste`
checkbox. The code will then be put in the clipboard when you click a
book icon and you can paste it where you want in the editor window.

Below is some code created in Radiant will generate regression output
for the `diamonds` data. There are plots of histograms and a scatterplot
/ heatmap of the price of diamonds versus carats. The colors in the plot
reflect the clarity of the diamond.

```{r fig.width=7, fig.height=4}
result <- regression(dataset = 'diamonds', reg_dep_var = 'price', reg_indep_var = 'carat')
summary(result)
plot(result, reg_plots = 'hist')
```

```{r fig.width=7, fig.height=7}
visualize(dataset = 'diamonds', viz_xvar = 'carat', viz_yvar = 'price', viz_type = 'scatter', viz_color = 'clarity')
```

